\textbf{Computational Fuzzy Extractors}

### 2013-06-14 CompFuzzExt.tex
Changing parameter settings to 2rhoq+1

\item $|W|$: The length of the source.  
\item $t$: Number of errors that can be supported.  
\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
\item $q$: The size of the field.  
\item $\rho$: The fraction of the field needed for error sampling.  
\item $m$: The size of each number of samples in the LWE instance.  
\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
We will split the source $|W|$ into $m$ blocks each of size $\rho q$~(that is, $|W| = m\log \rho q$).  We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.  As stated above we have three constraints:
\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.
\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
\item Minimize entropy loss of the construction.  We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.  We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.  Substituting, one has $m\log \rho q = k \log q$.
Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
n_0&< n -k \\
t&\leq d \log n\left(\frac{m}{n}-2\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+\sigma}m\\
m\log \rho q &= k \log q
Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
n_0&< n - k\\
t&\leq d\log n\left(\frac{m}{n}-2\right)\\
m \log 2n^{1/2+\sigma}m &= k \log n^f
%\xnote{$ m \log 2n^{1/2+\sigma}m = n \log n^f$}
This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
n_0&< n -k \\
t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma} m}{\log n}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.  Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
n_0&< n -k \\
m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}
%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+\sigma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+\sigma}}{\log n}$}
Note that $f$ is at a constant in $n$.
Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+\sigma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.  We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).  The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.  In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.  This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.  %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.

\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
\label{ssec:block params}
We repeat parameter settings for block fixing sources.  We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.  We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
\begin{align*}
n_0&< n -k  -\alpha -\beta\\
t&\leq d \log n\left(\frac{m}{n}-2\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+\sigma}m\\
m\log \rho q &= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k - \alpha -\beta\\
t&\leq d\log n\left(\frac{m}{n}-2\right)\\
m \log 2n^{1/2+\sigma}m &= k \log n^f
\end{align*}
As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n -k  - \alpha - \beta \\
t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma} m}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.  Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
\begin{align*}
n_0&< n/3 -  \log n\\
m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}
\end{align*}

Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+\sigma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
\end{align*}

>>>>

\begin{itemize}
\item $|W|$: The length of the source.  
\item $t$: Number of errors that can be supported.  
\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
\item $q$: The size of the field.  
\item $\rho$: The fraction of the field needed for error sampling.  
\item $m$: The size of each number of samples in the LWE instance.  
\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
\end{itemize}
We will split the source $|W|$ into $m$ blocks each of size $2\rho q+1$~(that is, $|W| = m\log (2\rho q+1)$).  We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.  As stated above we have three constraints:
\begin{itemize}
\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.
\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-2)$.
\item Minimize entropy loss of the construction.  We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.  We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.  Substituting, one has $m\log 2\rho q+1 = k \log q$.
\end{itemize}
Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
\begin{align*}
n_0&< n -k \\
t&\leq d \log n\left(\frac{m}{n}-2\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+\sigma}m\\
m\log (2\rho q +1)&= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k\\
t&\leq d\log n\left(\frac{m}{n}-2\right)\\
m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
\end{align*}
%\xnote{$ m \log 2n^{1/2+\sigma}m = n \log n^f$}
This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n -k \\
t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma} m+1}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.  Finally we assume that $m$ is the minimum value such that $t \leq d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
\begin{align*}
n_0&< n -k \\
m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
f &= \frac{m}{k}\frac{\log 4n^{1/2+\sigma}m+1}{\log n} = \frac{g(c+2d)}{d}\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
\end{align*}
%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+\sigma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+\sigma}}{\log n}$}
Note that $f$ is at a constant in $n$.
Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
\end{align*}

Note, that $f> \frac{m}{k}\geq \frac{m}{n} \geq \frac{(c/d+2)n}{n} \geq 3$ as long as $c>d$~(the condition that $m\geq 3n$ is also required for \lemref{lem:i t poly time} to hold).  Since $\rho q = 2n^{1/2+\rho }m = O(n^{5/2})$ in our setting $\rho = O(n^{-1/2})$.  Thus, for large enough settings of parameters $\rho$ is less than $1/10$ as required by \lemref{lem:uniform LWE decision}.

Furthermore, we get decoding using $O(n^{4d+3})$ $\Fq$ operations.  We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).  The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.  In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.  This analysis proceeds similarly when we desire a linear stretch instead of $m\log (2\rho q +1)= k\log q$.  %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.

\subsection{Parameter Settings for \thref{thm:lossless block sketch log}}
\label{ssec:block params}
We repeat parameter settings for block fixing sources.  We now have $m+\alpha$ as the number of samples, while $n + \alpha+\omega(1)$ is the number of variables.  We can support any setting where $t, n, q, \rho, m, k, \alpha$ satisfy the following constraints~(for $\beta = \omega(1)$ and constants $d, f$):
\begin{align*}
n_0&< n -k  -\alpha -\beta\\
t&\leq d \log n\left(\frac{m}{n}-2\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+\sigma}m\\
m\log (2\rho q+1)&= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k - \alpha -\beta\\
t&\leq d\log n\left(\frac{m}{n}-2\right)\\
m \log (4n^{1/2+\sigma}m +1)&= k \log n^f
\end{align*}
As before we can support any setting any $n, t, m, \alpha$ that satisfy these equations for $\beta = \omega(1)$ and constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n -k  - \alpha - \beta \\
t&\leq d\log n\left(\frac{ m }{n} -2\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma} m+1)}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k, \alpha = n/3$ and $\beta = \log n$.  Finally we assume that $m$ is the minimum value such that $t \leq  d \log n(m/n-2)$~(that is, there are only as many dimensions as necessary for decoding using \lemref{lem:i t poly time}):
\begin{align*}
n_0&< n/3 -  \log n\\
m &= \frac{(c+2d)n \log n}{d \log n} = \frac{(c+2d)n}{d}\\
f &= \frac{m}{k}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n} = \left(\frac{3(c+2d)}{d}\right)\frac{\log (\frac{4(c+2d)}{d} n^{3/2+\sigma}+1)}{\log n}
\end{align*}

Assuming $n/3-\log(n)> n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log (4n^{1/2+\sigma}m+1)}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
\end{align*}

\bnote{As before explain why $\rho<1/10$ condition is satisfied}
